\begin{clues}{Across}
    \clue{1} London {\blank} (drink made with Earl Grey tea, vanilla syrup, and steamed milk)
    \clue{4} The current one is the Holocene
    \clue{9} Photoshop option
    \clue{13} Stein contents, perhaps
    \clue{14} Singer-songwriter Bonoff
    \clue{15} Music to a diva's ears
    \clue{16} Reality show about an ex-Housewife's fishing-tackle business?
    \clue{19} At any time
    \clue{20} Word that begins nearly every "Seinfeld" episode title
    \clue{21} Units on a light-bulb box
    \clue{22} "My Ántonia" author Cather
    \clue{24} Novak Djokovic, for one
    \clue{25} Reality show on which contestants have to pretend to sing whatever song comes up on their iPads?
    \clue{29} Topping for chilaquiles
    \clue{30} Western Hemisphere alliance: Abbr.
    \clue{31} Three-time Tony winner Kazan
    \clue{33} Charisse of "Silk Stockings"
    \clue{34} Terms in office
    \clue{38} Org. for the Cleveland Guardians
    \clue{39} Many-{\blank} (variegated)
    \clue{41} Atlantis docked with it in 19Emphasis indicators, for short
    \clue{42} Reality show that rewards the most careless competitor?
    \clue{44} Richard of "Sommersby" and "Autumn in New York"
    \clue{48} "Hey, me too!"
    \clue{49} "Open" memoirist Andre
    \clue{50} "Au revoir, {\blank} amis!"
    \clue{53} Word on some rubber stamps
    \clue{54} Reality show about queens trying to look glamorous while working on a small farm?
    \clue{57} Rugged rocks
    \clue{60} Zola who wrote "J'Accuse!"
    \clue{61} Is blessed with
    \clue{62} "If you insist . . ."
    \clue{63} Air Force Academy student
    \clue{64} Home-office expense
\end{clues}
\vspace{\cluesep}
\begin{clues}{Down}
    \clue{1} No. 1 choice
    \clue{2} Patron saint of Norway
    \clue{3} Frequent collaborator of Richard Pryor
    \clue{4} Squeeze (out)
    \clue{5} To a degree
    \clue{6} Harry Potter or Anne Shirley, say
    \clue{7} Game involving a rope
    \clue{8} {\blank} radio
    \clue{9} Streusel-topped dessert
    \clue{10} Far from everyday
    \clue{11} Appliance that gets a lot of use on Thanksgiving
    \clue{12} "Not for me, thanks"
    \clue{15} Quote on a dust jacket
    \clue{17} Tap issues
    \clue{18} "The magic word"
    \clue{23} Exam with a max score of 1Betelgeuse, for one
    \clue{24} Two-pointer from close range
    \clue{25} Woo
    \clue{26} 1992 Robert Rodriguez film whose title figure is a travelling guitarist
    \clue{27} Meg of "The Big Chill"
    \clue{28} Coll. or univ.
    \clue{29} Midriff muscles
    \clue{32} Author of the cookbook "Louisiana Real and Rustic," to fans
    \clue{35} "Well done!"
    \clue{36} YouTuber and "So You Think You Can Dance" judge JoJo
    \clue{37} Very long time
    \clue{40} Busch Gardens locale
    \clue{43} "{\blank}, Take the Wheel" (Carrie Underwood song)
    \clue{45} Password's partner
    \clue{46} Key on an antique cash register
    \clue{47} Rockets' paths
    \clue{50} Sikh spiritual leader
    \clue{51} On {\blank} with (comparable to)
    \clue{52} Molly, more formally
    \clue{53} Neighbor of Azerbaijan
    \clue{55} Resolute {\blank} (longtime fixture of the Oval Office)
    \clue{56} "Hey, wait a {\blank}!"
    \clue{58} Procure
    \clue{59} 
\end{clues}